---
title: "Homework_Stats_2"
output:
  html_document:
    df_print: paged
    theme: united
    toc: yes
  html_notebook: default
  word_document:
    toc: yes
  pdf_document: default
name: Aman Singh
---

# Problem_1

## Problem_1.a

summarized the dataset women containing 2 variables & 15 observations. The two variables are Height( measured in inches) &  weight (measured in lbs)

```{r}
summary(women)
```

## Problem_1.b
Declared Height & weight by variables and applied the formula of BMI (assigning a variable to it)

```{r}
y<-women$height
Z<-women$weight
BMI<-(z*703)/(y^2)
print(BMI)
```

## Problem_1.c

Added the column BMI to the dataframe women

```{r}
women ['BMI']=BMI
summary(women)
```

## Problem_1.d


```{r}
MeanBMI<-sum(BMI)/length(BMI)
calculatedvar<-1/(length(BMI)-1)*sum((BMI-MeanBMI)^2)
SDBMI<-sqrt(calculatedvar)
skewness<-(1/(length(BMI)))*sum((((BMI-MeanBMI))*(1/SDBMI))^3)
kutosis<-(length(BMI))*sum((BMI-MeanBMI)^4)*(1/sum((BMI-MeanBMI)^2))
print(MeanBMI)
print(calculatedvar)
print(SDBMI)
print(skewness)
print(kutosis)
```

## Problem_1.e

Skewness is more than 0; we can safely say we have a right skewed dataset BMI.

## Problem_1.f

A kurtosis more than 3 (positive excess) is the opposite situation - leptokurtic and over here we have 9.58 as the kurtosis,leptokurtic.



# Problem_2

## Problem_2.a

Loaded the table from the saved destination

```{r}
dataset<-read.table("filtered_qb.csv",sep=",",header = TRUE)
```


## Problem_2.b

The mean in both the cases are almost similar, but the variance/ SD in case of actuals is pretty high indicating the increased separation of actuals values from mean.
In case of skewness, the projections is more skewed toward the right as compared to actuals.
In case of kurtosis, the projections is more leptokurtic as compared to actuals.

```{r}
summary(dataset)
y<-dataset$projections
z<-dataset$actuals
MenProj<- sum(y)/length(y)
calculatedvarproj<-1/(length(y)-1)*sum((y-MenProj)^2)
SDBMIProj<-sqrt(calculatedvarproj)
skewness1<-(1/(length(y)))*sum((y-MenProj)^3)*(1/SDBMIProj^3)
kutosis1<-(length(y))*sum((y-MenProj)^4)*(1/sum((y-MenProj)^2))
MenAct<- sum(z)/length(z)
calculatedvaract<-1/(length(z)-1)*sum((z-MenAct)^2)
SDBMIAct<-sqrt(calculatedvaract)
skewness2<-(1/(length(z)))*sum((z-MenAct)^3)*(1/SDBMIAct^3)
kutosis2<-(length(z))*sum((z-MenAct)^4)*(1/sum((z-MenAct)^2))
print(MenProj)
print(MenAct)
print(calculatedvarproj)
print(calculatedvaract)
print(SDBMIProj)
print(SDBMIAct)
print(skewness1)
print(skewness2)
print(kutosis1)
print(kutosis2)


```



## Problem_2.c
c. Describe the data that was collected.

```{r}
our.five.sum<-fivenum(dataset$actuals)
print(our.five.sum)
print(median(our.five.sum))
```

## Problem_2.d

The plot function does give a positive correlation with somehwat strictly positive for initial values of projections and actuals.
```{r}
boxplot(dataset$projections)
boxplot(dataset$actuals)
plot(dataset$projections,dataset$actuals)
hist(dataset$projections)
hist(dataset$actuals)
hist(dataset$actuals,breaks=10)
hist(dataset$actuals,breaks=30)

```
 
 

# Problem_3
```{r}
library(ISwR)
View(cars)
```

## Problem_3.a

There are 50 observations in this dataset comprising two variables speed and distance.

## Problem_3.b

```{r}
copy_cars<- cars
```
## Problem_3.c

```{r}
time<-(copy_cars$dist)/(copy_cars$speed)
copy_cars ['time']<- time
print(copy_cars)

```

## Problem_3.d

```{r}
head(copy_cars,14)
```

## Problem_3.e

```{r}
median(copy_cars$time)
```

## Problem_3.f

```{r}
our.five.sum2<-fivenum(copy_cars$time)
summary(our.five.sum2)
View(our.five.sum2)
Q1<-our.five.sum2[2]
Q3<-our.five.sum2[4]
print(Q1)
print(Q3)

```

