---
title: "Homework_Stats_3"
output:
  html_document:
    df_print: paged
    theme: united
    toc: yes
  html_notebook: default
  word_document:
    toc: yes
  pdf_document: default
name: Aman Singh
---
###Note that n in this workbook is used for Intersection and U is used for Union at appropriate places.

## Problem 1a

Since A and B are independent events P(A n B) = P(A).P(B)

Let's consider P(A n B') = P(A) - P(A n B)
                         = P(A) - P(A).P(B)
                         = P(A). [1 - P(B)]
                         = P(A). P(B')

We can say that A and B' are independent events.

Theoretically when A and B are independent, the occurence of one events tells nothing about occurence of the second event. When you say something about the occurence of an event you are in fact implicitly talking about the complement of it. So when A and B are independent, the complement is also independent.
                         

## Problem 1b

```{r}
# Let a be the probability of P(A)
a <- 2/3
a
# Let b be the probability of P(B)
b <- 4/7
b
```

###Note that n in this workbook is used for Intersection and U is used for Union at appropriate places.

### Problem 1b.a

Max Value of P(A n B)

Theoretically, this happens when the smaller probability event is subset of the larger probability event, in which case the intersection is maximum. And the intersection is nothing but the smaller probability event(Imagine a venn diagram with the description)


```{r}
min(a,b)
```

### Problem 1b.b

Min Value of P(A n B)

Generally, P(A n B) is minimum when they are mutually exclusive events (when there is no intersection) and is 0.
However, we need to check the constraint whether A U B is within the the sample space or not. Which means as long as a+b <= 1 A n B can have a min value of 0. What if a+b is exceeding 1? It suggests that there exists some intersection and the best case to have A n B a min value is when A U B just makes up 1.

max(P(A U B)) = max(a + b - P(A n B))
1 = a + b - min(A n B)
min(A n B) = a+b - 1

if a+b-1 is becoming negative you can safely say the min(A n B) as 0.

```{r}
max(0, (a+b)-1)
```

In a different case, give yourself some values to a and b such that a+b <= 1 and understand more. 


### Problem 1b.c

Max value of P(A n B')

P(A n B') = A - P(A n B)

max[P(A n B')] = max[A - P(A n B)]
               = A - min[P(A n B)]
               = a - max(0, (a+b)-1)    [Refer problem 1b.b]

```{r}
a - max(0, (a+b)-1)
```

### Problem 1b.d

Min value of P(A n B')

P(A n B') = A - P(A n B)

max[P(A n B')] = min[A - P(A n B)]
               = A - max[P(A n B)]
               = a - min(a,b)           [Refer problem 1b.a]

```{r}
a - min(a,b)
```


### Problem 1b.e

Max value of P(A U B)

max[P(A U B)] = max[P(A) + P(B) - P(A n B)]
              = P(A) + P(B) - min[P(A n B)]
              = a + b - max(0, (a+b)-1)     [Refer problem 1b.b]

```{r}
a + b - max(0, (a+b)-1)
```

### Problem 1b.f

Min value of P(A U B)

min[P(A U B)] = min[P(A) + P(B) - P(A n B)]
              = P(A) + P(B) - max[P(A n B)]
              = a + b - min(a,b)          [Refer problem 1b.a]

```{r}
a + b - min(a,b)
```


### Problem 1b.g

Max value of P(A/B)

P(A/B) =  P(A n B)/P(B)
max[P(A/B)] = max[P(A n B)/P(B)]
            = max[P(A n B)]/P(B)
            = min(a,b)/b
            
```{r}
min(a,b)/b
```
            

### Problem 1b.h

Min value of P(A/B)

P(A/B) =  P(A n B)/P(B)
min[P(A/B)] = min[P(A n B)/P(B)]
            = min[P(A n B)]/P(B)
            = max(0, (a+b)-1)/b
            
```{r}
max(0, (a+b)-1)/b
```


## Problem 2

P(P|D): Probability that the test is positive for the disease given that the person has the disease
P(P|D'): Probability that the test is positive for the disease given the person does not have the disease
P(D)  : Probability that the patient has the disease0000..0




.01.14.142.1424.12
.412

4.1..

455
.1.
1.1..45
45
..
.12

P(P|D) = 0.95 
P(P|D')=0.01
P(D) = 0.005

  P(D)  : Probability that the patient does not have the disease
  P(D') = 1 - P(D) = 1-0.005 = 0.995


To Calculate:
P(D|P) : Probability that the person has the disease given the test is positive

P(D|P) = {P(P|D).P(D)}/ {P(P|D).P(D) + P(P|D').P(D')}
        = 0.95 * 0.005 / (0.95 * 0.005) + (0.01 * 0.995)

```{r}
(0.95 * 0.005) / ((0.95 * 0.005) + (0.01 * 0.995))
```

## Problem 3

P(A): Probability that aircraft transmitter is made by company A
P(B): Probability that aircraft transmitter is made by company B
P(C): Probability that aircraft transmitter is made by company C

P(A) = 0.8
P(B) = 0.15
P(c) = 0.05

P(D|A): Probability that aircraft transmitter is defective given that it is made by company A 
P(D|B): Probability that aircraft transmitter is defective given that it is made by company B
P(D|C): Probability that aircraft transmitter is defective given that it is made by company C

P(D|A) = 0.03
P(D|B) = 0.065
P(D|C) = 0.09


## Problem 3a  

Probability that the aircraft transmitter is made by Company A is:
P(A) = 0.8
  
## Problem 3b

If a randomly selected aircraft transmitter is tested and is found to be defective, find the probability that it was made by Company A.
    
P(A|D) = {P(A).P(D|A)} / {P(D|A).P(A) + P(D|B).P(B) + P(D|C).P(C)}
       =  {0.8 * 0.03} / {(0.8 * 0.03) +  (0.065 * 0.15) +  (0.09 * 0.05)}

```{r}
(0.8 * 0.03) / ((0.8 * 0.03) +  (0.065 * 0.15) +  (0.09 * 0.05))
```


# Problem 4

       
## Problem 4a


As each of the investments are independent of each other, the probability of 3rd investment is 1/2

P(3rd Investment to be successful) = 1/2


## Problem 4b


In the given statement, there are only two possible scenarios:

Saple space with given conditions = {SSS, FFF}
favorable = {SSS}
required probabilty = 1/2

## Problem 4c
Let S be the successful investment and N be the non-successful event

If we look at the truth table below, there are three cases wherein there are exactly 2 Success (#2,#3,#5):

1.SSS
2.SSN
3.SNS
4.SNN
5.NSS
6.NSN
7.NNS
8.NNN

Out of #2,#3,#5,
 #3 and #5 has success in the third attempt.
 Hence, P(Success in the third investment | 2 of the 3 events are successful) = 2/3

This question is not clearly mentioned if at least two of the three investments is successful or only two of the three investments is successful. There by both interpretations are given full grade. 

So below solution is also acceptable.
P(Success in the third investment | at least 2 of the 3 events are successful) = 2/4 = 1/2


## Problem 4d

Suppose now that the probability that investment 1 is successful is 0.845, the probability that
investment 2 is successful is 0.5505, and the probability that investment 3 is successful is 0.4.
Consider these two events: A: two of the three investments are successful, and B: investment
3 is successful. Are these events independent? Why or why not?


Let S1, S2 and S3 be the events that the first, second and third investments are successful.
P(S1) = 0.845,  P(S2)= 0.5505, P(S3)= 0.4

P(A)     : Probability that the two of the three investments are successful 
P(B)     : Probability of event that third investment is successful
P(A U B) : Probability that two of the three investments are successful and third investment is successful
      
To prove that event A and event B are independant, 
P(A|B) = P(A)

P(A n B) =  P(S1')P(S2)P(S3) + P(S1)P(S2')P(S3) 

```{r}
(0.845 * 0.4495* 0.4) + (0.155 * 0.5505 *0.4)
```

         
P(B)     = P(S1')P(S2')P(S3) + P(S1')P(S2)P(S3) + P(S1)P(S2')P(S3) + P(S1)P(S2)P(S3)

```{r}
(0.845 * 0.5505 * 0.4)+(0.845 * 0.4495 * 0.4)+(0.155 * 0.5505 * 0.4)+(0.155 * 0.4495 * 0.4)
```


P (A|B)   = P(A n B)/P(B)


```{r}
0.1861/0.4		
```


P(A)      = P(S1)P(S2')P(S3) + P(S1)P(S2)P(S3') + P(S1')P(S2)P(S3')

```{r}
(0.845* 0.5505* 0.6)+(0.845* 0.4495* 0.4)+(0.155* 0.5505*0.4)
```

P(A|B) = P(A). Hence, Event A and Event B independent to each other




# Problem_1

## Problem_1.a

Is the following statement true or false? If true, explain why, and if false, come up with a counter example. If A and B are independent then A and B' are independent.

P(A|B)= P(A∩B)/P(B)
 Since we know, A and B are independent then  
 P(A∩B)= P(A)*P(B) 
and P(B)= 1- P(B')
 P(A∩B)= P(A) - P(A) P(B')  
So,

P(A) P(B') = P(A) - P(A∩B)-----(a) 
 
Since A∩B'  =  A - A∩B and A∩B ⊂ A, 
 
&
P(A∩B') = P(A) - P(A∩B)--------(b)
 
With (a) and (b), P(A∩B') = P(A) P(B') which signals A and B' are independent.

 
## Problem_1.b

Suppose P(A) = 2/3 and P(B) = 4/7. 

Assuming A and B are not independent events.

(a) What is the maximum value of P(A∩B)? 
 
 The maximum value will occur when A completely covers B, in that case, the venn diagram will show B inside A.
  P(A∩B)= 4/7

(b) What is the minimum value of P(A∩B)? 

 The minimum value will occur when A and B have minimum overlapping between them.
 P(AUB)= P(A)+P(B)-P(A∩B)
 For Minimum P(AUB) should be maximum and should cover the whole venn diagram. 
 P(AUB)=1= 2/3 + 4/7 -  P(A∩B)
 or,  P(A∩B)=26/21 - 1= 5/21
 thus, the minimum value = 5/21

(c) What is the maximum value of P(A∩B')? 

  Since, P(A∩B') = P(A) - P(A∩B)
 The maximum value will occur when P(A∩B) is minimum , in that case, P(A∩B')= 2/3 - 5/21= 0.42857 ~ 0.43

(d) What is the minimum value of P(A∩B')?

 Since, P(A∩B') = P(A) - P(A∩B)
 The minimum value will occur when P(A∩B) is maximum , in that case, P(A∩B')= 2/3 - 4/7= 0.09524 ~ 0.095

(e) What is the maximum value of P(A∪B)? 

Maximum value of P(A∪B) occurs when P(A∩B) is minimum, thus maximum value will be 1.

(f) What is the minimum value of P(A∪B)? 
The minimum value occurs when P(A∩B) is maximum, thus minimum value will be= 1-4/7= 3/7

(g) What is the maximum value of P(A|B)? 
The maximum value of P(A|B) occurs when P(A∩B) is maximum and in our case that value is 4/7. Thus, maximum value of P(A|B)= (4/7)/(4/7)= 1

(h) What is the minimum value of P(A|B)?
The minimum value of P(A|B) occurs when P(A∩B) is minimum and in our case that value is 5/21. Thus, minimum value of P(A|B)= (5/21)/(4/7)= 5/12

Assuming A & B are independent events.

(a) What is the maximum value of P(A∩B)? 

 The only Possible value of P(A∩B) = P(A)xP(B)= (2/3)x(4/7)=8/21
 
(b) What is the minimum value of P(A∩B)? 

 The only Possible value of P(A∩B) = P(A)xP(B)= (2/3)x(4/7)=8/21
 
(c) What is the maximum value of P(A∩B')? 

  Since, P(A∩B') = P(A) - P(A∩B)
 The only value will be = (2/3) - (8/21)= 6/21

(d) What is the minimum value of P(A∩B')?

  Since, P(A∩B') = P(A) - P(A∩B)
 The only value will be = (2/3) - (8/21)= 6/21

(e) What is the maximum value of P(A∪B)? 

P(A∪B) can take only one value = P(A)+P(B)- P(A)xP(B)= 2/3 + 4/7 - 8/21 =18/21

(f) What is the minimum value of P(A∪B)? 

P(A∪B) can take only one value = P(A)+P(B)- P(A)xP(B)= 2/3 + 4/7 - 8/21 =18/21

(g) What is the maximum value of P(A|B)? 

P(A|B) can take only 1 value = P(A)= 2/3

(h) What is the minimum value of P(A|B)?

P(A|B) can take only 1 value = P(A)= 2/3


# Problem_2

A laboratory blood test is 95 percent eﬀective in detecting a certain disease when it is, in fact, present. However, the test also yields a “false positive” result for 1 percent of the healthy persons tested. (That is, if a healthy person is tested, then, with probability 0.01, the test result will imply he has the disease.) If 0.5 percent of the population actually has the disease, what is the probability a person has the disease given that his test result is positive?

Assuming the total population to be 1000 and then creating contingency table. We get



                  Positive               Negative
Disease Present   (0.95x5)               (0.05x5)                   5 --- Total Disease Present


Disease Absent    (0.01X995)            (0.99X995)                 995---Total Disease Absent    
                    14.7                                          1000

So, the total positives given by the test = 14.7 
and out of that only 4.75 have actually the disease.
Thus, the probability of a person having the disease when his test is positive = (4.75)/(14.7)= 0.3232
There is 32.32% chance a person has the disease given his test result is positive.


# Problem_3

An aircraft transmitter is a device designed to transmit a signal in the case of a crash. Company A makes 80% of the aircraft transmitters, Company B makes 15% of them, and the Company C makes the other 5%. The transmitters made by Company A have a 3% rate of defect, those made by Company B have a 6.5% rate of defect, and those made by Company C have a 9% rate of defect.
a. If an aircraft transmitter is randomly selected from the general population of all aircraft transmitters, ﬁnd the probability that it was made by Company A.

If we suppose the total transmitters manufactured = 100
the probability that it was made by Company A = 80/100 = 0.8


b. If a randomly selected aircraft transmitter is tested and is found to be defective, ﬁnd the probability that it was made by Company A

                A      B          C
Defective   (0.03*80) (0.065*15) (0.09*5)  3.825
Non-Defective                             96.175
               80     15          5        100

Probability that the defective is from A = Number of defective produced by A/ Total defectives produced 
= 2.4/3.825 = 0.6275

# Problem_4

Suppose your ﬁrm has three potential investments. The investments are either sucessful or not. Suppose that each investment has probabilty 1/2 of being successful.

a. What is the probability that the third investment is successful?

For the 3rd investment to be succesfull = All 3 are successfull + Except 1st investment all are successfull + Only the 3rd is successfull. = (1/2)^3 + (1/2)^3 + (1/2)^3 = (3/8)

b. What is the probability that the third investment is successful, given that the three investments are either all successful or all not successful?

P(3rd is successfull| All or none are success)
P(C|(S or US))= P(C and (S or US ))/P(S or US)= P(C and S) or P(C and US)/(1/4) = [(1/8)+0]/(1/4) = 1/2
P(3rd is successfull| All or none are success)
There will only be 2 cases either all are successful or unsuccessfull.
And only in 1 case we can have the third investment successful. Thus the probability of picking that case which has 3rd investment successfull = 1/2.

c. What is the probability that the third investment is sucessful, given that two of the three investments is successful?

P(3rd is successfull| only 2 are success)

Since, it's given that 2 of the three investments are successful. The number of ways of choosing the two investments = 3C2 = 3
1st case, when 1 & 2 successfull, 3 unsuccessful
Or
2nd case, when 1 & 3 successfull, 2 unsuccess
Or
3rd case, when 2 & 3 successfull, 1 unsuccess

Out of these three ways there are only two ways in which the third investment is successful.

Probability = 2/3

d. Suppose now that the probability that investment 1 is successful is 0.845, the probability that investment 2 is successful is 0.5505, and the probability that investment 3 is successful is 0.4. Consider these two events: 
A: two of the three investments are successful, 
1st case, when 1 & 2 successfull, 3 unsuccessful. 
Or
2nd case, when 1 & 3 successfull, 2 unsuccess     
Or
3rd case, when 2 & 3 successfull, 1 unsuccess   


B: investment 3 is successful. 

For the 3rd investment to be succesfull 
All 3 are successfull 
Or
Except 1st investment all are successfull
Or
Only the 3rd is successful 

Are these events independent? Why or why not?

We notice that in A & B, there is one instance (Investment 1 is unsuccessfull rest successfull) which is common to both. In case of independent events, occurrence of one shouldn't affect the occurrence of the other, but in our case occurrence/non-occurrence of this instance (Investment 1 is unsuccessfull rest successfull) may cause changes in the other event. 
