---
title: "Homework_Stats_7"
output:
  html_document:
    df_print: paged
    theme: united
    toc: yes
  html_notebook: default
  word_document:
    toc: yes
  pdf_document: default
name: Aman Singh
---
#Problem 1

Let X be a random variable that is normally distributed with mean 10 and standard deviation 2.
Let Y be a random variable that is normally distributed with mean 15 and standard deviation 1.
Let Z be a random variable that is 2 · X + 3 · Y .
a. What is the expected value of X? Answer this question without simulation.
b. What is the expected value of Y ? Answer this question without simulation.
c. What is the expected value of Z? Answer this question without simulation.
d. Use simulation to estimate the correlation of Y and Z. What is your estimate of the correlation?
e. Using your estimate from the previous part, and without additional simulation, what is the
variance of Y + Z?
f. Simulate Y + Z. What is the estimated variance of Y + Z based on the simulation?

## Problem 1a

the expected value is the weighted average of the random variable X = 10

## Problem 1b

the expected value is the weighted average of the random variable Y = 15
## Problem 1c

the expected value is the weighted average of the random variable Z = 2*10+3*15= 65
Variance of (Z)= (2^2)x(Var(X)+(3^2)x(Var(Y) +2x2x3xcov(X,Y)

```{r}
set.seed(100)
x<-rnorm(10,10,4)
y<-rnorm(10,15,1)
print(covariance_xy<-cov(x,y))
print(Variance_Z<-4*4+9*1+12*covariance_xy)
```

## Problem 1d

```{r}
set.seed(100)
y<-rnorm(10,15,1)
z<-rnorm(10,65,4.69)
cor(y,z)
COr_sim<-mean(replicate(1000,cor(rnorm(10,15,1),rnorm(10,65,4.69))))
COr_sim
```


## Problem 1e
Y+Z = Y+2X+3Y = 2X+4Y

Variance of (Y+Z)= (2^2)x(Var(X)+(4^2)xVar(Y) +2x2x4xcov(X,Y)

cov(X,Y)= corr
```{r}
print(Variance_New<-4*4+16*1+16*covariance_xy)
```


## Problem 1f

```{r}
set.seed(100)
y<-rnorm(1,15,1)
z<-rnorm(1,65,4.69)
mean(y+z)
print(Sum_Sim<-mean(replicate(1000,mean(rnorm(1,15,1)+rnorm(1,65,4.69)))))
print(Variance_sim<-mean(replicate(1000,Variance_New)))
      
```

#Problem_2

In class we discussed Chebyshev’s rule, which states that regardless of how the data are distributed,
at least (1 − 1/k2) · 100% of the distribution of a variable will fall within k standard deviations of
the mean (for k > 1).
a. For k = 2 and for k = 3, what is the maximum amount of the distribution that will fall within
k standard deviations of the mean?
b. Find a distribution that minimizes the portion of the distribution (mass for discrete, density
for continuous) that falls within 2 standard deviations of the mean. How does this compare
with Chebyshev’s rule? Explain.
c. Find a distribution that minimizes the portion of the distribution (mass for discrete, density
for continuous) that falls within 3 standard deviations of the mean. How does this compare
with Chebyshev’s rule? Explain.


##Problem_2a

for k=2 , atleast (1-1/4)*100 % = 75% of the distribution will fall within k standard deviations and
for k=3, atleast (1-1/9)*100% = 88.89% of the distribution.

Thus, for k=2 or 3 maximum 100% of the distribution will fall within k standard deviations.

##Problem_2b
for k=2,
We can go for discrete mass function with the values keep checking the condition with chebychev principle.
For this reason the results are usually weak. The value given by the theorem is a lower
bound only. That is, we know that the probability of a random variable falling
within two standard deviations of the mean can be no less than 3/4, but we never
know how much more it might actually be. Only when the probability distribution
is known can we determine exact probabilities. For this reason we call the theorem
a distribution-free result. When specific distributions are assumed, as in future
chapters, the results will be less conservative. 


```{r}
sim_values_2b <- replicate (1000, runif(1, min=-1 , max= +1)) 
i <- 0
counter<- 0
for ( i in 1: 1000)
{ 
  if ((sim_values_2b[i] <= mean(sim_values_2b) + 2*sd(sim_values_2b)) && (sim_values_2b[i] >= mean(sim_values_2b) - 2*sd(sim_values_2b)))
      
      { counter<- counter+1 }    
         
} 

counter/ length(sim_values_2b) 

```

##Problem_2c
for k=3,
We can go for discrete mass function with the values keep checking the condition with chebychev principle.

```{r}
sim_values_2c <- replicate (10000, runif(1, min=-1 , max= +1)) 
i <- 0
counter<- 0
for ( i in 1: 10000)
{ 
  if ((sim_values_2c[i] <= mean(sim_values_2c) + 2*sd(sim_values_2c)) && (sim_values_2c[i] >= mean(sim_values_2c) - 2*sd(sim_values_2c)))
      
      { counter<- counter+1 }    
         
} 

counter/ length(sim_values_2c) 
```




















#Problem_3

Suppose that the true distribution of the median salary in an affluent suburb of New York is
normally distributed with mean $120,000 and standard deviation $10,000.
a. Suppose I take a random sample of 10 individuals from the area. What is the distribution of
the mean salary in the sample? Please indicate the parameters of the distribution as well as
the distribution type.
b. Simulate 1000 samples of size 10. What is the average value of the sample mean? What is
the standard deviation of the sample mean? How does that compare with your answer to the
previous part.
c. Simulate 10000 samples of size 10. What is the average value of the sample mean? What is
the standard deviation of the sample mean? How does that compare with your answer to the
previous parts.
d. Simulate 100000 samples of size 10. What is the average value of the sample mean? What
is the standard deviation of the sample mean? How does that compare with your answer to
the previous parts.
e. Now suppose you take a random sample of size 30. What is the distribution of the mean salary
in the sample? Please indicate the parameters of the distribution as well as the distribution
type.
f. Simulate 100000 samples of size 30. What is the average value of the sample mean? What
is the standard deviation of the sample mean? How does that compare with your answer to
the previous parts.

##Problem_3.a

As per the lecture, the sample of 10 individuals will also be normally distributed.

With the mean of the sample = 120,000
Standard deviation = 10,000/sqrt(10) = 3162.28


##Problem_3.b

```{r}
set.seed(100)
x<-rnorm(10,120000,10000)
print(Sim_sample_mean<-mean(replicate(1000,rnorm(10,120000,10000))))
print(Sim_sample_sd<-sd(replicate(1000,rnorm(10,120000,10000))))
```

It's coming out to be larger as compared to the previous one.

##Problem_3.c

```{r}
set.seed(100)
x<-rnorm(10,120000,10000)
print(Sim_sample_mean2<-mean(replicate(10000,rnorm(10,120000,10000))))
print(Sim_sample_sd2<-sd(replicate(10000,rnorm(10,120000,10000))))
```

##Problem_3.d

```{r}
set.seed(100)
x<-rnorm(10,120000,10000)
print(Sim_sample_mean3<-mean(replicate(100000,rnorm(10,120000,10000))))
print(Sim_sample_sd3<-sd(replicate(100000,rnorm(10,120000,10000))))
```
##Problem_3.e

As per the lecture, the sample of 30 individuals will also be normally distributed.

With the mean of the sample = 120,000
Standard deviation = 10,000/sqrt(30) = 1825.74



##Problem_3.f

```{r}
set.seed(100)
x<-rnorm(30,120000,10000)
print(Sim_sample_mean<-mean(replicate(100000,x)))
print(Sim_sample_sd<-sd(replicate(100000,x)))
```
The sd is coming out to be larger than the manually calculated sd.

#Problem_4
You are looking to estimate the proportion of pet owners that have pet insurance. You know
from experience that at least 10% have pet insurance. A statistician takes a random sample of
1000 pet owners and creates a 95% confidence interval for the proportion of pet owners that have
pet insurance. The confidence interval is [0.23, 0.31]. For each part below, if you can answer the
question, provide the answer and an explanation. If you cannot answer the question, provide details
on why you cannot.
a. What is the probability that the true population proportion of pet owners that have pet
insurance is above 0.1?
b. What is the probability that the true population proportion of pet owners that have pet
insurance is between [0:23; 0:31]?
c. David Bergman has decided to create a procedure for building interval estimates. He takes a
random sample of 100 pet owners. If the proportion of pet owners in the sample that have
pet insurance is less than 0.1, he reports an interval estimate of [0.0, 0.05]. If the proportion
of pet owners in the sample that have pet insurance is greater than or equal to 0.1, he reports
an interval estimate of [0.1, 1.0]. Ignoring the statistician’s test, but taking the rest of the
problem statement into account, what is the maximum probability that David Bergman’s test
reports an interval of [0.0, 0.05]?
d. Suppose the true proportion of pet owners that have pet insurance is 0.3. What is the
confidence level of David Bergman’s test?


##Problem_4a

It's given that there are going to be atleast 0.1 proportion, thus we can claim that the probability will be almost 1 as we have to consider 0.1 case too.

##Problem_4b
confidence interval doesn't signifies the true proportion, so it can't be calculated. 

##Problem_4c
a sample of 100 pet owners, indicative probability. 

Let, X be the number of pet owners that have a pet insurance. 
We shall be modelling X as a binomial variable with n= 1000 and pi= 0.1. 


```{r}

sim_values_4c <- replicate (1000, rbinom(1, size= 100, prob= 0.1)) 

counter <- 0

for (i in 1: length(sim_values_4c)) 
  
{ if(sim_values_4c[i]<10)
{ counter <- counter+1}
  
} 

counter/ length(sim_values_4c) 



```

##Problem_4d

Here, given that neam proportion= 0.3. 
And, we know that sd_proportion = sqrt ( ( pi* (1-pi) ) / (sample size) ) 

```{r}
pi_4d <- 0.3 

sd_proportion <- sqrt( ( pi_4d * (1-pi_4d) ) / 100 )  

```

Now, David Bergman test is as confident as the possibility of selecting a sample of size 100 which includes the true mean. 

So, we find probability of selecting a sample which shall include the true proportion. 

```{r}
1- pnorm (0.1, 0.3, sd_proportion) 
```
